\documentclass[a4paper,11pt]{extarticle}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks,pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{calc}
\usepackage[top=0.55in, left=0.57in, right=0.57in]{geometry}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\textheight}{11in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]
%-------------------------
% Custom commands
\newcommand{\resumeSkillItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeItem}[1]{
	\item\small{
		#1 \vspace{-1.2pt}
	}
}

\newcommand{\resumeItemWithoutTitle}[1]{
	\item\small{
		{\vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}
    \item
		\begin{tabular*}{1\linewidth}{l@{\extracolsep{\fill}}r}
			\textbf{#1} & #2 \\
			\textit{#3} & \textit{#4} \\
		\end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubItem}[2]{\resumeSkillItem{#1}{#2}\vspace{-5pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{
    \begin{itemize}[leftmargin=0.15in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-3pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

%-----------------------------
%%%%%%	CV STARTS HERE	%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{{\LARGE John Gunerli}}
	\\ (470) 388-2623 & 
    \underline{\href{https://github.com/hakancangunerli}
        {github.com/hakancangunerli}} \\
        \underline{\href{mailto:hakancangunerli@gatech.edu}
        {hakancangunerli@gatech.edu}} &
        \underline{\href{https://www.linkedin.com/in/hakancangunerli}
        {linkedin.com/in/hakancangunerli}}		
\end{tabular*}

\section{Education}
	\resumeSubHeadingListStart
		\resumeSubheading
			{Georgia Institute of Technology}{Atlanta, GA}
            {B.S. in Computer Science
                CGPA: 3.72 }
			{Graduating Dec 2023}
	\resumeSubHeadingListEnd
\section{Experience}
	\resumeSubHeadingListStart
      
\resumeSubheading
            {Georgia Institute of Technology}
            {\textbf{Aug 2022 -- Present}}
            {Undergraduate Computer Vision Researcher --- LIDAR Lab}
            {Atlanta,GA}
            \resumeItemListStart
			\resumeItem{Developed a computer vision script using OpenCV's HOG detector for whole-body detection.}
            \resumeItem{Implemented human detection and human distance detection through depth sensors with respect to the camera location, including accurately measuring the distance of detected humans.}
            \resumeItem{Contributed to the development of a real-time human detection system for CASSIE, the GT LIDAR Group's robot system for human trajectory detection.}
		\resumeItemListEnd   

  
     
		\resumeSubheading
            {Georgia Institute of Technology \& Emory University}
            {\textbf{May 2022 -- Sep 2022}}
		    {Undergraduate Student Assistant: Software Development and Architecture}
            {Remote}
		\resumeItemListStart
			\resumeItem{Designed and built a website from scratch using Typescript, Figma, and React.}
			\resumeItem{Presented the design to Georgia Tech and Emory University faculty for approval throughout the development process, meeting HIPAA standards and hosted at AWS.}
   \resumeItem{Gathered and evaluated information from faculty to tailor the website to their needs, including creating visualization dashboards and implementing secure authentication systems for researchers.}
		\resumeItemListEnd

 \resumeSubheading
            {University of Georgia}
            {\textbf{May 2021 -- Jun 2022}}
            {Undergraduate Student Assistant: Frontend Lead and Head of UI/UX}
            {Athens, GA}
            \resumeItemListStart
\resumeItem{Acted as Frontend Development Lead and Undergraduate Student Assistant for the CiliaWeb project, an NSF-funded integrated platform for foundational and reproducible ciliary beat pattern analysis.}
\resumeItem{Led a team of three people in the frontend development department for the project.}
\resumeItem{Oversaw the complete redesign of the website using Figma, React, Ant Design, and Bootstrap.}
\resumeItem{Utilized Figma, React, and ExpressJS to create an improved user interface and user experience.}
		\resumeItemListEnd   

  

   \resumeSubheading
            {University of Georgia}
            {\textbf{Aug 2021 -- Dec 2021}}
            {Undergraduate Robotics Researcher --- HERO Lab}
            {Athens, GA}
            \resumeItemListStart
			\resumeItem{Experienced with ClearPath Robotics' TurtleBot 2, Rover Robotics' OpenRover, and CMU's LoCoBot.}
            \resumeItem{Developed scripts to teleoperate and create simultaneous maps (SLAM) using gmapping software in ROS.}
            \resumeItem{Collaborated with graduate students and faculty to overcome challenges and troubleshoot research obstacles.}
		\resumeItemListEnd  
    

     \resumeSubheading
            {Peero}
            {\textbf{Jan 2021 -- Aug 2021}}
            {Co-Founding Team \& Startup Technical Program Manager}
            {Remote}
		\resumeItemListStart
\resumeItem{Oversaw product development for the startup, managing projects involving software, hardware, and internal communication.}
\resumeItem{Led product strategy and roadmap creation, working closely with the business team and in-house designer, including collaboration with CTO on technology development and software build decisions. }
\resumeItem{Facilitated agile development and made data-driven decisions to ensure the timely delivery of high-quality products.}
		\resumeItemListEnd
     \resumeSubheading
            {Turkiye Is Bankasi}
            {\textbf{Sept 2020 -- Oct 2020}}
            {Software Engineering Intern}
            {Remote}
		\resumeItemListStart
\resumeItem{Completed an internship as a Software Engineer at the payment processing team at SoftTech, the software subsidiary of Turkiye Is Bankasi.}
\resumeItem{Collaborated with a team of five software engineers on the development of a Point-of-Sale orchestration platform, utilizing MongoDB and .NET systems in the development process.}
\resumeItem{Applied Angular and C\# in the creation of a visual JSON connection program, utilizing the frontend and backend, respectively.}
		\resumeItemListEnd
\resumeSubHeadingListEnd
\section{Skills Summary}
	\resumeSubHeadingListStart
		\resumeSubItem{Languages}
            {\hspace{0.2mm}~~~~~~Python, C++20, Java, Julia, TypeScript, HTML/CSS}
		\resumeSubItem{Packages}
            {\hspace{0.2mm}~~~~~~~~~sklearn, Streamlit, Matplotlib, NumPy, BeautifulSoup, Pandas, OpenCV, transformers, JSON}
            \resumeSubItem{Tools}
            {\hspace{0.2mm}~~~~~~~~~~~~~~Figma, Sketch, Adobe XD, JIRA, Trello, ClickUp, Asana, AirTable, Notion, Linux/Unix}
            \resumeSubItem{Areas of Focus}
            {\hspace{0.2mm}Human-Centered Computing (HCI, HRI), Artificial Intelligence (ML and CV)}          
	\resumeSubHeadingListEnd
\end{document}